Co-moving stars in \textsl{Gaia DR1}

### 2016-10-05 paper/ms.tex
more words in the intro

Two stars moving with similar full-space velocity vectors (``co-moving stars'')
are either remnants of a dispersing stellar system or are a widely-separated
binary star system. In either case, co-moving stars are of great interest for
studying chemical uniformity and star formation processes, the destruction of
star clusters and dwarf galaxies, and the tidal field and small-scale properties
of the mass distribution in the Milky Way. To date, thousands of candidate
co-moving star pairs have been identified by searching for stars with common
proper motions (\citealt{Luyten:1979,Poveda:1994,Allen:2000,Gould:2003,
Chaname:2004,Lepine:2007,Alonso-Floriano:2015}).
% Cite:
% https://ui.adsabs.harvard.edu/#abs/2012ApJ...757..170A/abstract
% https://ui.adsabs.harvard.edu/#abs/2012AJ....144..102T/abstract
% https://ui.adsabs.harvard.edu/#abs/2014ApJ...790..158A/abstract

@@

@@

>>>>

Two stars moving with similar full-space velocity vectors (``co-moving stars'')
are either members of a widely-separated stellar multiplet, or remnants of a
dispersing stellar system.

Widely-separated binary stars are weakly bound binary star systems with
semi-major axes larger than $a \gtrsim 10^{-3}~{\rm pc}$. It is generally
assumed that the stars in a wide binary form from gas with the same chemical
composition and are separated enough that there is no interaction or minimal
cross-pollution as the more massive star evolves (\citealt{todo}). Because the
binding energy of these systems is so low, if wide binary stars survive for many
Gigayears their existence alone places limits on the tidal field of the Galaxy
(\citealt{todo}) and the graininess of the gravitational field (\citealt{todo}).
In this picture, a remaining puzzle is how these systems survive the dense
stellar environments of the birth clusters in which they form. Wide binaries are
therefore important tools for studying small-scale star formation and the
large-scale Galactic mass distribution. These stars will appear to be co-moving
with velocity differences comparable to the binary orbital velocity at the
given separation.

At the largest separations, $a \gtrsim 1~{\rm pc}$, co-moving stars are likely
either remnants of disrupting stellar systems or young wide binary stars: at
these extreme separations, the Galactic tidal field would disrupt binary stars
within $t_{\rm disrupt} \lesssim XX~{\rm Gyr}$. Unbound open clusters with
velocity dispersions $\sigma_v \lesssim 1~\kms$ in the Galactic disk disrupt
quickly leaving small streams of stars with the same chemical abundances
(\citealt{chemicaltaggingstuff}). Disrupting or disrupted globular clusters and
dwarf galaxies also produce streams of stars with similar chemical properties
but with larger velocity differences (\citealt{streampeeps}). Stars from such
systems at similar orbital phases will appear to be co-moving with velocity
differences comparable to the internal velocity dispersions, $\sigma_v \approx
1$--$10~\kms$.

To date, thousands of candidate co-moving star pairs have been identified by
searching for stars with common proper motions (\citealt{Luyten:1979,
Poveda:1994, Allen:2000, Gould:2003, Chaname:2004, Lepine:2007,
Alonso-Floriano:2015}). \todo{how is our search different? (1) we have distance, (2) bigger volume than Hipparcos, (3) we use the data properly, (4) we don't cut on distance or on magnitude of proper motion -- we cut on parallax S/N}
% Cite:
% Tokovinin & Lepine 2012
% https://ui.adsabs.harvard.edu/#abs/2012ApJ...757..170A/abstract
% https://ui.adsabs.harvard.edu/#abs/2012AJ....144..102T/abstract
% https://ui.adsabs.harvard.edu/#abs/2014ApJ...790..158A/abstract

% Many searches find things close in angular separation, but need pms / distance

@@

In either case, co-moving stars are of great interest
for studying the destruction of star clusters and dwarf galaxies, the tidal
field and small-scale properties of the mass distribution in the Milky Way, and
chemical uniformity and star formation processes.

@@

\section{Results 1: A catalog of candidate wide binaries}

\todo{Galactic context / orbits}

\section{Results 2: Star clusters and cluster remnants}

\section{Conclusions}
